Meta-analysis

### 2020-08-31 03_Prep_data.Rmd
Rename files for order in bookdown Rename importData file. maybe delete later

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq())
```

```{r import_data}
PM_MB_means <- read.csv("cache/1911_PM_MB_means&Ygains.csv")

source("R/same.R") # matches each element of a vector and does not return NAs
```

@@

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
   summarise(DMI_treatments = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   select(!fungicide_ai) %>%
   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

The experiment summaries report either standard deviation, least square differences or no error term (`NA`). 
First we will convert LSD and standard deviation to sample variance.
Then we will impute variances for the trials, which did not report any form of variance (`NA`).

@@

We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted to select the T-crit value in the equation. 
Our data contained 30 degrees of freedom which equates to a 'T-crit' value of 1.697.

![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)

`Tcrit` is the T critical value for which there is significant difference between two groups.
This value is the same for both trials "mung1112/01" and "mung1112/02".

```{r LSD_2_Sampling_Variance}
Tcrit <- 1.697 # 0.05 and DFw = 30

for (i in Trials$trial_ref) {
   DFw <-
      sum(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) -
      length(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) # degrees of freedom within groups

   LSD <-
      PM_MB_means[PM_MB_means$trial_ref == i, ]$yield_error[1]

   V_yield <-
      (PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates[1] * 
          (LSD / Tcrit) ^ 2) / 2 
   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates)) {
      if (j == 1) {
         Sv <-
            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates))
      } # reset Sv vector if this is the first loop

      Sv[j] = V_yield /
         PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[j]

@@

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_means %>%
   filter(Y_error_type == "stdev") %>%
   select(trial_ref) %>%
   distinct()

# calculate the Sampling variance from the standard deviation
# standard error of the mean equals the standard deviation divided by the square
#  root of the number of samples
# Sv <- sem^2 <- stdev/sqrt(n)
# Sampling variance equals the square of the standard error.
# Sv <- (stdev/sqrt(n))^2

# Therefore

for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
   if (j == 1) {
      Sv <-
         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
   }# create empty vector at first iteration with length of j

   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
}

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
   "SamplingVariance"
```

@@

```{r Var_mean_sqaures}
# redefine sample variance calculated from mean square
PM_MB_means$vi <-
   PM_MB_means$Y_Msquare /
   (PM_MB_means$n)

PM_MB_means %>%
   ggplot(aes(x = grain_yield.t.ha., y = vi)) +
   geom_point()
```

We see here that the sample variance generally decreases or has no association with the grain yield.
This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares, which defines between trial variation and is the more generic error term.

```{r Var_MeanSquarePlot}
PM_MB_means %>%
   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
   geom_point()
```

## Reduce data set to required variables

Let's tidy up the data set into a data frame of only the variables, which are required for the analysis.

First remove the irrelevant columns/variables.
Then calculate fungicide application timing variables relative to the first sign of disease.
Entries with `NA` in the grain yield or powdery mildew severity are also removed from the data.

```{r clustered_fungicide_applications}
source("R/slimming_PM_dat.R") # see R script for the code, which reduces the data.

slim_PM_dat %<>%
   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
   filter(!is.na(grain_yield.t.ha)) %>%
   filter(!is.na(PM_final_severity))
```

### Cluster fungicide applications

We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.

@@

   - **Late**: First fungicide application was four or more days after first sign of disease being observed. 
Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.

```{r cluster}
slim_PM_dat %<>%
   mutate(
      cluster_1 = case_when(
         fungicide_timing_1 < 0 ~ "Early",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 ~ "Recommended",
         TRUE ~ "Late"
      )
   ) %>%
   mutate(
      cluster_2 = case_when(
         is.na(fungicide_timing_2) ~ NA_character_,
         fungicide_timing_2 < 13 ~ "Early",
         fungicide_timing_2 >= 13 &
            fungicide_timing_2 < 17 ~ "Recommended",
         TRUE ~ "Late"
      )
   ) %>%
   mutate(
      cluster_3 = case_when(
         fungicide_timing_3 < 14 ~ "Early",
         is.na(fungicide_timing_3) ~ NA_character_,
         TRUE ~ "Recommended"
      )
   )
```

Let's look at these clusters to see where we have the most degrees of freedom.

```{r cluster_clusters}
clusters <-
   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])

for (i in 1:nrow(clusters)) {
   if (i == 1) {
      clusters$n <- NA
      clusters$n_x_trial <- NA
   }

   clusters[i, "n"] <-
      nrow(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
                          same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
                          same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),])

   clusters[i, "n_x_trial"] <-
      length(unique(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
                                   same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
                                   same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),
                                "trial_ref"]))

knitr::kable(clusters)
```

From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. We will reduce this to 6 levels within one variable.

Single sprays of either:

   a) early,

   b) recommended timing,

   c) late.

Two or more sprays where the first spray was either:

   d) early,

   e) recommended timing,

   f) late.

```{r simple_clusters}
slim_PM_dat <- slim_PM_dat %>%
   mutate(
      spray_management = case_when(
         fungicide_timing_1 < 0 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Early",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Recommended",
         fungicide_timing_1 >= 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Late",
         fungicide_timing_1 < 0 &
            !is.na(fungicide_application_2) ~ "Early_plus",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            !is.na(fungicide_application_2) ~ "Recommended_plus",
         fungicide_timing_1 >= 4 &
            !is.na(fungicide_application_2) ~ "Late_plus",
         TRUE ~ "Other"
      )
   )

slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
            c(
               "fungicide_timing_1",
               "fungicide_timing_2",
               "fungicide_timing_3",
               "spray_management"
            )] <- "control"
```

@@

```{r tableSprayManagement}
table(slim_PM_dat$spray_management)
```

@@

```{r simpler_clusters_remove}
slimmer_PM_dat <-
   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]
```

@@

@@

Earlier we noted there were different doses of propiconazole, which might influence our analysis.
Let's check this by comparing a linear mixed effect model including and excluding dose.
We already have a factor breaking down the dose in the `trial` variable.
Let's make a new one without dose.

```{r dose_test}
slimmer_PM_dat$trial_noDose <- paste(slimmer_PM_dat$trial_ref, slimmer_PM_dat$year,
                 slimmer_PM_dat$location,slimmer_PM_dat$host_genotype,
                 slimmer_PM_dat$row_spacing,sep = "_")

cbind(Dose = head(slimmer_PM_dat$trial),
      NoDose = head(slimmer_PM_dat$trial_noDose)) %>%
   kable()
```

@@

```{r dose_lmer}
m1 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)

m2 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial_noDose),
        data = slimmer_PM_dat)

anova(m1, m2)
```

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m1`.
We will retain dose as a variable inside the `trial` factor.

```{r saveDat}
slimmer_PM_dat <-
   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
```

## Disease pressure factor

We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot.
We will create two categories, `lowD` and `highD`.
We will use the median `AUDPC` to separate the trials into these two groups.

```{r DiseasePressure}
slimmer_PM_dat$D_pres <- NA_character_

Trial_Dpress <- slimmer_PM_dat %>%
   group_by(trial_ref) %>%
   filter(fungicide_ai == "control") %>%
   summarise(AUDPC_C = mean(AUDPC_m, na.rm = TRUE))

median_AUDPC <-
   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
median_AUDPC

sort(Trial_Dpress$AUDPC_C)

for (i in unique(slimmer_PM_dat$trial_ref)) {
   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
      next()
   }

   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
   {
      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
   } else{
      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
      } else{
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
            NA_character_
      }
   }
}
```

Let's have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.

```{r plot_disease_pressure}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot() +
   xlab("Disease pressure") +
   ylab("Grain yield (t/ha)")
```

From this plot we see that in the trials with high disease pressure tended to produce lower yields. 
There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.

@@

We may want to consider row spacing in the trials.
However one of the locations has `NA` as the row spacing.
For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.

```{r assign_row_spacing_missing}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
```

>>>>

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq()
)
```

```{r import_data}
load("cache/PreliminaryData.Rdata")
source(here("R/same.R")) # matches each element of a vector and does not return NAs
```

## Subset to Trials containing DMI fungicides

```{r filterDMI_trials}
DMI_Trials <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref) %>%
   pull()

PM_MB_dat <- 
   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
```

Now remove any non-DMI treatments or controls
```{r}
PM_MB_dat <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control" |
             fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")
```

@@

```{r variance_types}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, year , Y_error_type) %>%
   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported",
         align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

The experiment summaries report either standard deviation, least square differences. 
First we will convert LSD and standard deviation to sample variance.

@@

We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).

```{r LSD_2_Sampling_Variance}
Tcrit <- 2.042

for (i in Trials$trial_ref) {
   DFw <-
      sum(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) -
      length(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) # degrees of freedom within groups

   LSD <-
      PM_MB_dat[PM_MB_dat$trial_ref == i, ]$yield_error[1]

   V_yield <-
      (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] * 
          (LSD / Tcrit) ^ 2) / 2 
   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

   for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates)) {
      if (j == 1) {
         Sv <-
            vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates))
      } # reset Sv vector if this is the first loop

      Sv[j] = V_yield /
         PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates[j]

@@

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_dat %>%
   filter(Y_error_type == "stdev") %>%
   select(trial_ref) %>%
   pull()

PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"] <- 
   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"]^2

PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,]$Y_error_type <-
   "SamplingVariance"

```

@@

```{r Var_mean_sqaures}
PM_MB_dat %>%
   ggplot(aes(x = grain_yield.t.ha., y = yield_error)) +
   geom_point()
```
No association between yield and sample variance, this might be due to the unpredictable nature of mungbeans.

Lets look at the association between mean squares and yield to see if there is a more typical association between yield and variance.

```{r Var_MeanSquarePlot}
PM_MB_dat %>%
   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare/replicates)) +
   geom_point()
PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),]

```

## Classifying fungicide treatment

First we need to calculate the time between the first sign of disease and the fungicide treatments.

```{r clustered_fungicide_applications}
PM_MB_dat %<>%
   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)

```

To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made.

@@

   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

The number of sprays need also be defined.

```{r}
data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
           n_sprays = rep(c("Single", "Two - Three"), each = 3),
           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
                                       "1 - 3 days after first sign of Powdery Mildew",
                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
   kable()
```

```{r simple_clusters}
PM_MB_dat <- PM_MB_dat %>%
   mutate(
      spray_management = case_when(
         fungicide_timing_1 < 0 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Early",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Recommended",
         fungicide_timing_1 >= 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Late",
         fungicide_timing_1 < 0 &
            !is.na(fungicide_application_2) ~ "Early_plus",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            !is.na(fungicide_application_2) ~ "Recommended_plus",
         fungicide_timing_1 >= 4 &
            !is.na(fungicide_application_2) ~ "Late_plus",
         TRUE ~ "Other"
      )
   )

PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
            c(
               "fungicide_timing_1",
               "fungicide_timing_2",
               "fungicide_timing_3",
               "spray_management"
            )] <- "control"
```

@@

```{r tableSprayManagement}
table(PM_MB_dat$spray_management)
```

@@

```{r simpler_clusters_remove}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(spray_management != "Early_plus")
```

@@

## Trial factor
We have a number of variable which could introduce variation in our analysis. 
We will combine these variables into a single variable called `trial` which will help us define the between trial variation.

```{r define_trial}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(trial = paste(trial_ref, year, location, host_genotype,
                        row_spacing, sep = "_")) %>%
   select(trial_ref, trial, everything())
```

@@

Earlier we noted there were different doses of propiconazole, which might influence our analysis.
Let's add the dose variable to the `trial` variable then compare linear mixed effect models including and excluding dose in the trial variable.
We already have a factor breaking down the dose in the `trial` variable.
Let's make a new one without dose.

```{r define_Dose}
table(PM_MB_dat$dose_ai.ha)

PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(dose = case_when(
      dose_ai.ha == 0 ~ "control",
      dose_ai.ha <= 70 ~ "lowDose",
      dose_ai.ha > 70 ~ "highDose",
      TRUE ~ NA_character_
   ))

```

```{r dose_test}
PM_MB_dat <-
   PM_MB_dat %>%
    mutate(trial_dose = paste(trial_ref, year, location, host_genotype,
                        row_spacing,dose , sep = "_"))

cbind(NoDose = head(PM_MB_dat$trial),
      Dose = head(PM_MB_dat$trial_dose)) %>%
   kable()
```

@@

```{r dose_lmer}
m_noDose <-
   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = PM_MB_dat)

m_dose <-
   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
           (1 | trial_dose),
        data = PM_MB_dat)

anova(m_noDose, m_dose)
```

Using the model without dose produces a lower AIC and we find no significant difference between models.
We will not use dose as a defining variable in `trial`.

Remove columns which are not needed
```{r saveDat}
PM_MB_dat <-
   PM_MB_dat %>%
   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
             fungicide_application_7)) 
```

@@

We may want to consider row spacing in the trials.
However one of the locations has `NA` as the row spacing.
```{r}
PM_MB_dat%>%
   filter(is.na(row_spacing))%>%
   select(trial_ref,year, location, row_spacing,spray_management,host_genotype, fungicide_ai)
```

For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.

```{r assign_row_spacing_missing}
PM_MB_dat[is.na(PM_MB_dat$row_spacing),"row_spacing"] <- 0.33
```

# Perhaps move below to post analysis, analysis

### Mungbeans age and yield saved

The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
Let's have a look at the age of each trial when powdery mildew infected it.
We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity when it became infected.

```{r age_andYield}
dat1 <- PM_MB_dat %>%
   mutate(days2PM = first_sign_disease - planting_date) %>%
   arrange(desc(days2PM)) %>%
   select(
      trial_ref,
      year,
      location,
      spray_management,
      days2PM,
      grain_yield.t.ha,
      yield_gain,
      prop_yield_gain,
      AUDPC_m,
      D_pres,
      PM_final_severity
   )
dat1
```

From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
Therefore I will not inspect, `AM1304` (Marys Mount), which only trialled an early, prophylactic spray.

We can see that the crops which were likely the most mature, did not show large yield gains, in particular:

   * Hermitage 2019  
   * Premer  
   * Goolhi  
   * Millmerran

Let's look at this in a quick box plot. 
We will only look at trials where powdery mildew set in 60 days after planting, when the physiological maturity was likely flowering.

```{r ageBoxPlot}
dat1 %>%
   filter(days2PM >= 60) %>%
   filter(spray_management != "control" &
             trial_ref != "AM1304") %>%
   group_by(trial_ref, spray_management) %>%
   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
   geom_boxplot() +
   scale_fill_usq() +
   geom_hline(yintercept = 0)
```

We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application given the values of the recommended _plus treatment were predominantly lower than zero.

For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.

```{r PM40_2_59_days}
dat1 %>%
   filter(days2PM < 60 &
             days2PM >= 40) %>%
   filter(spray_management != "control") %>%
   group_by(trial_ref, spray_management) %>%
   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
   geom_boxplot() +
   scale_fill_usq() +
   geom_hline(yintercept = 0)
```

We can see here all four experiments benefited, on average, from more than one spray.

Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.

```{r whatAreTheAges}
dat2 <- PM_MB_dat %>%
   mutate(
      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
   ) %>%
   select(location, year, flower, pod, late_pod) %>%
   distinct() %>%
   arrange(desc(flower))

index1 <-
   apply(dat2, 1 , function(X)
      ! all(is.na(X[c("flower", "pod", "late_pod")])))

dat2[index1,]
as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
```

We can see that flowering and podding can be variable, and depend on the cumulative degree days.
However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.

### 2020-08-31 04_MetaAnalysis.Rmd
Rename files for order in bookdown Rename importData file. maybe delete later

ggplot(slimmer_PM_dat, aes(x = as.factor(year), fill = spray_management)) +
   geom_bar(position = "dodge2") +
   scale_fill_usq(name = "Spray Management") +
   xlab("Year")

@@

```
<!-- I don't like this graph, it is hard to read given that different widths don't translate to anything meaningful -->

@@

```{r netgraphGW}
netgraph(
   net_con,
   plastic = FALSE,
   col = usq_cols("support orange"),
   thickness =  "number.of.studies",
   points = FALSE,
   col.points = usq_cols("usq charcoal"),
   cex.points = 1,
   number.of.studies = TRUE,
   cex.number.of.studies = 1,
   col.number.of.studies = "black",
   bg.number.of.studies = usq_cols("support orange"),
   multiarm = FALSE,
   col.multiarm = usq_cols("support turquiose"),
   pos.number.of.studies = 0.5
)
```

@@

```{r Save_meta_data, eval=FALSE}
save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts,contrast_Ssum,file =
        here("cache/Meta-analysisData.Rdata"))
```

#### Powdery mildewMBM comparison -- Delete
One aspect we would like to consider is how the results of this meta-analysis compares to how the PowderyMildewMBM estimates the effect of fungicide applications on grain yields.
Below we create a data frame of the mitigation factors for each spray scenario so we can compare them to the outcomes of the meta-analysis.
```{r compare2PowderyMildewMDM}

PMBM <- 
   data.frame(Sprays = c(rep(1,20), rep(2,20)),
              Disease = rep(c(rep("NotPresent", 5),
                          rep("LowerCanopy", 5),
                          rep("MidCanopy", 5),
                          rep("UpperCanopy", 5)),2),
              CropMaturity = rep(c("Vegetative", "Budding", "Flowering",
                                   "EarlyPod", "LatePod"), 8),
              mitigation = c(0.57, 0.855, 0.95,0.95,0.95,
                             0.45995, 0.52919,0.5530,0.390,0.1642,
                             0.291258,0.351051, 0.2454,0.1409,0.4717,
                             0,0.059597,0.093034,0.0682476,0.0215584,
                             0.95,0.95,0.95,0.95,0.95,
                             0.766588,0.6991,0.55042,0.390056,0.1642,
                             0.485429,0.390,0.2454,0.140904,0.0471684,
                             0.0791,0.086068,0.093034,0.0682476,0.0215584))

# what is the mean age of the plant in our data when disease first occurs and we apply the first spray?
source("R/import_data.R")
PM_MB_dat <- import_data()
mean(PM_MB_dat$first_sign_disease - PM_MB_dat$planting_date, na.rm =TRUE) # 46.3 days (which is when the plant is flowering)

#What proportion of the yield was saved?
1 - (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[3]))
1- (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[4]))

PMBM %>%
   filter(CropMaturity == "Flowering")

```
To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields.

>>>>

ggplot(slimmer_PM_dat, aes(x = as.factor(year), fill = spray_management)) +
   geom_bar(position = position_dodge2(width = 0.9, preserve = "single")) +
   scale_fill_usq(name = "Spray Management") +
   xlab("Year")

@@

@@

```{r netgraphGW}
netgraph(
   net_con,
   plastic = FALSE,
   col = usq_cols("support orange"),
   thickness =  "number.of.studies",
   points = FALSE,
   col.points = usq_cols("usq charcoal"),
   cex.points = 1,
   number.of.studies = TRUE,
   cex.number.of.studies = 1,
   col.number.of.studies = "black",
   bg.number.of.studies = usq_cols("support orange"),
   multiarm = FALSE,
   col.multiarm = usq_cols("support turquiose"),
   pos.number.of.studies = 0.4
)
```

@@

```{r Save_meta_data, eval=FALSE}
save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts, contrast_Ssum, 
     file = here("cache/Meta-analysisData.Rdata"))
```
